Avancement du stage

### 2025-05-20 presentation.qmd
Mise à jour app

```{python}
#| label: minimize_gev_aic_map
title = "Modèle minimisant l'AIC"
echelle = "quotidien"
mod_dir = Path(config["gev"]["modelised"]) / echelle
obs_dir = Path(config["gev"]["observed"]) / echelle

>>>>

```{python}
#| label: minimize_gev_aic_map
echelle = "quotidien"
season = "hydro"
title = f"Modèle minimisant l'AIC (SAISON {season})"
mod_dir = Path(config["gev"]["modelised"]) / echelle / season
obs_dir = Path(config["gev"]["observed"]) / echelle / season
